---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# isaiahr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/isaiahr)](https://CRAN.R-project.org/package=isaiahr)
<!-- badges: end -->

The goal of `isaiahr` is to wrap core demonstration functionality extracted from [Forecasting: Principles and Practice, version 3][fpp3], by Rob J. Hyndman and George Athanasopoulos of Monash University, Australia.

[fpp3]:https://otexts.com/fpp3/

The name of the package derives from Chapter 1 of Forecasting: Principles and Practice. It quotes Isaiah chapter 41, verse 23, "[Shewe the things that are to come hereafter, that wee may knowe that ye are gods][isaiah-41-23]." (King James version, 1611)

[isaiah-41-23]:https://www.kingjamesbibleonline.org/1611_Isaiah-Chapter-41/#23

## Installation

You can install the development version of `isaiahr` like so:

```r
devtools::install_github("data-science-r/isaiahr")
```

## Example

This is a basic example:

```{r example}
library(isaiahr)

tsibble::as_tsibble(USAccDeaths) %>%
  stl_components("value") %>%
  fabletools::autoplot()
```

## Futures, Progress

The Monash forecasting tool-kit makes parallel processing with futures easier. The `fabletools` package makes use of futures automatically if it finds the `future` package attached during model estimation.

## Rserve

Work in progress.
